Individuals Make a Difference: An Olympics Medal Prediction Model Based on LightGBM

### 2025-01-27 论文/PAPER.tex
LAST

\title{Together, Individuals Make a Difference}  % 标题

@@

\subsection{Our work}
We preprocess the data provided before analyzing matches and mainly utilize 3 models. The specific work was as follows.
\begin{figure}[H]
	\centering
	\includegraphics[width=16cm]{img/da.png}
	\caption{Workflow of Our Methodology}
	\label{fig:aa}
\end{figure}

@@

To demonstrate the differences in the levels of countries in previous Olympic Games (i.e. national level), we employed the \textbf{KMeans++} algorithm. Based on the number of gold, silver, and bronze medals, as well as the total medal count of each country in past Olympics, we categorized the countries into five levels. These 5 levels, L1, L2, L3, L4, and L5, form a partition of the sample set X (the total number of gold, silver, and bronze medals won by countries in previous Olympic Games).
\begin{equation}
G_{i} \cap G_{j}=\emptyset, \bigcup_{i=1}^{5} G_{i}=X
\end{equation}
After the classification, the distribution of countries across the 5 levels is shown in the figures:
\begin{figure}[H]
	\centering
	\includegraphics[width=12cm]{img/Level1.png}
	\caption{Scatter plot of national level classification (based on KMeans++ clustering algorithm)}
	\label{fig:aa}
\end{figure}

@@

\section{Task 1:Medal Prediction Model Based on LightGBM}
\subsection{Medal Table}
The medal table is influenced by various factors. To predict the standings for the next Olympics, we considered key factors identified during data preprocessing, such as nation level, participating athletes, country-specific event strengths, and adjustments to medal counts.

@@

We input the previously obtained data into LightGBM for iterative model training. After training, we input the factors affecting the predictions for the next edition into the model, ultimately obtaining the predicted medal table for the 2028 Summer Olympics in Los Angeles, USA, are shown in Figure \ref{fig:aa}.
%奖牌榜预测图
\begin{figure}[H]
	\centering
	\includegraphics[width=11cm]{img/Predict.png}
	\caption{Medal Count Prediction}
	\label{fig:aa}
\end{figure}

@@

\section{Task 2:Great Coach Effect}
\subsection{Verification of the Great Coach Effect}
The Great Coach effect can cause significant differences in the performance of relevant countries in corresponding events. To collect evidence of changes caused by this effect, we use a \textbf{Bayesian Changepoint Detection (BEAST)} model.

@@

\section{Task 3:Other Original Insights}

@@

\section{Conclusion}
\begin{itemize}
		\item \textbf{Task1}

@@

	\item \textbf{Task2}

@@

Additionally, the \textbf{CUSUM} algorithm helped identify weak events for several countries, such as France’s decline in sailing, Sweden’s waning dominance in athletics and shooting, and Germany’s emerging strength in swimming, which later showed signs of decline. Based on these findings, we recommend hiring specialized coaches to help maintain or regain competitive advantages in these events.
	\item \textbf{Task3}

>>>>

\title{Individuals Make a Difference:

	An Olympics Medal Prediction Model Based on LightGBM}  % 标题

@@

\subsection{Our Work}
We preprocess the data provided before analyzing matches and mainly utilize 3 models. The specific work was as follows.
\begin{figure}[H]
	\centering
	\includegraphics[width=16cm]{img/da.png}
	\caption{Workflow of Our Methodology}
	\label{fig:aa}
\end{figure}

@@

To demonstrate the differences in the levels of countries in previous Olympic Games (i.e. national level), we employed the \textbf{KMeans++} algorithm. Based on the number of gold, silver, and bronze medals, as well as the total medal count of each country in past Olympics, we categorized the countries into five levels. These 5 levels, L1, L2, L3, L4, and L5, form a partition of the sample set X (the total number of gold, silver, and bronze medals won by countries in previous Olympic Games).
\begin{equation}
G_{i} \cap G_{j}=\emptyset, \bigcup_{i=1}^{5} G_{i}=X
\end{equation}

After the classification, the distribution of countries across the 5 levels is shown in the figures:
\begin{figure}[H]
	\centering
	\includegraphics[width=12cm]{img/Level1.png}
	\caption{Scatter plot of national level classification (based on KMeans++ clustering algorithm)}
	\label{fig:aa}
\end{figure}

@@

\section{Task 1: Medal Prediction Model Based on LightGBM}
\subsection{Medal Table}
The medal table is influenced by various factors. To predict the standings for the next Olympics, we considered key factors identified during data preprocessing, such as nation level, participating athletes, country-specific event strengths, and adjustments to medal counts.

@@

We input the previously obtained data into LightGBM for iterative model training. After training, we input the factors affecting the predictions for the next edition into the model, ultimately obtaining the predicted medal table for the 2028 Summer Olympics in Los Angeles, USA, are shown in the figure as follows.
%奖牌榜预测图
\begin{figure}[H]
	\centering
	\includegraphics[width=11cm]{img/Predict.png}
	\caption{Medal Count Prediction}
	\label{fig:aa}
\end{figure}

@@

\section{Task 2: Great Coach Effect}
\subsection{Verification of the Great Coach Effect}
The Great Coach effect can cause significant differences in the performance of relevant countries in corresponding events. To collect evidence of changes caused by this effect, we use a \textbf{Bayesian Changepoint Detection (BEAST)} model.

@@

\section{Task 3: Other Original Insights}

@@

\section{Conclusion}
\begin{itemize}
		\item \textbf{Task 1}

@@

	\item \textbf{Task 2}

@@

Additionally, the \textbf{CUSUM} algorithm helped identify weak events for several countries, such as France’s decline in sailing, Sweden’s waning dominance in athletics and shooting, and Germany’s emerging strength in swimming, which later showed signs of decline. Based on these findings, we recommend hiring specialized coaches to help maintain or regain competitive advantages in these events.
	\item \textbf{Task 3}
